The Unicode Cookbook \linebreak for Linguists

### 2018-07-30 book/chapters/introduction.tex
small caps in introduction

Breaking it down further, a script consists of \textsc{graphemes}, which are writing 
system-specific minimally distinctive symbols (see below). Graphemes may consist of one or more 
\textsc{characters}. The term \textsc{character} is overladen. In the linguistic terminology of writing
systems, a \textsc{character} is a general term for any self-contained element
in a writing system. A second interpretation is used as a conventional term for a unit in the Chinese writing
system \citep{Daniels1996}. In technical terminology, a \textsc{character} 
refers to the electronic encoding of a component in a writing system that has semantic 
value (see Section \ref{character-encoding-system}). Thus in this work we must navigate 
between the general linguistic and technical terms for \textsc{character} 
and \textsc{grapheme} because of how these notions are defined and how they relate at the intersection 
between the International Phonetic Alphabet and the Unicode Standard (Chapter \ref{ipa-meets-unicode}).

>>>>

Breaking it down further, a script consists of \textsc{graphemes}, which are writing 
system-specific minimally distinctive symbols (see below). Graphemes may consist of one or more 
\textsc{characters}. The term `character' is overladen. In the linguistic terminology of writing
systems, a character is a general term for any self-contained element
in a writing system. A second interpretation is used as a conventional term for a unit in the Chinese writing
system \citep{Daniels1996}. In technical terminology, a character}
refers to the electronic encoding of a component in a writing system that has semantic 
value (see Section \ref{character-encoding-system}). Thus in this work we must navigate 
between the general linguistic and technical terms for \textsc{character} 
and \textsc{grapheme} because of how these notions are defined and how they relate at the intersection 
between the International Phonetic Alphabet and the Unicode Standard (Chapter \ref{ipa-meets-unicode}).
